Dark matter halo shape in the Auriga simulations: radial dependence, time evolution and baryon disk alignment

### 2019-07-17 Document/paper.tex
edit

A common assumption in observational models of the MW DM halo is that
its minor axis is perfectly aligned with the stellar disk minor axis.
Although it is a reasonable assumption to guarantee the stability of
the galactic disk in simplified models of isolated galaxies, this
might not hold in an explicit cosmological context. 
To examine the degree of validity of this assumption we study in this
section the alignment between the eigenvectors of the inertia tensor of
stellar particles within $0.1R_{200}$ ($\approx 23\pm 2$ kpc) and the
eigenvectors of the dark matter halo shape.

>>>>

A common assumption in observational models of the MW DM halo is that
its minor axis is perfectly aligned with the stellar disk minor axis.
Although it is a reasonable assumption to guarantee the stability of
the galactic disk in simplified models of isolated galaxies, this
might not hold in an explicit cosmological context. 
To examine the degree of validity of this assumption we study in this
section the alignment between the eigenvectors of the inertia tensor of
stellar particles within $0.1R_{200}$ ($\approx 23\pm 2$ kpc) and the
eigenvectors of the dark matter halo shape.
All the measurements are done at $z=0$.

In Figure \ref{fig:cumulative_alignment} we summarize our main results
regarding these alignments with the halo shape measured at five
different radii.
The upper row shows the alignment of the halos in the DMO simulations
with the stellar disk in the MHD simulations.
The main objective of this measurement is to calibrate the radial
evolution of the DM halo shape. 
We find that the DM shape remains constant with radius.

The lower row shows
